---
title: "`r report_title`"
output:
  html_document:
    self_contained: true
    mathjax: null
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = max(4, length(unique(result$metrics$event_id)) * .3), dpi = 120
)
m <- report_metrics(result)
show_table <- function(d) {
  if (!nrow(d)) {
    return(htmltools::tags$p("No eligible records."))
  }
  DT::datatable(d,
    rownames = FALSE, escape = TRUE, filter = "top",
    extensions = "Buttons", options = list(
      dom = "Bfrtip", buttons = c("csv", "copy"),
      pageLength = 10, scrollX = TRUE, autoWidth = TRUE
    )
  )
}
```

<style>
h1.title { font-size: clamp(2rem, 4vw, 3rem); }
.dataTables_wrapper { max-width: 100%; overflow-x: auto; }
</style>

## Findings

```{r notices}
notices <- list()
if (isTRUE(result$metadata$provenance$synthetic)) {
  notices <- c(notices, list(htmltools::tags$p(
    class = "alert alert-info",
    htmltools::tags$strong("Synthetic demonstration. "),
    paste(
      "People, statements and measurements are invented. Planted",
      "patterns test the software; they do not validate a quality",
      "standard."
    )
  )))
}
if (is.null(result$policy)) {
  notices <- c(notices, list(htmltools::tags$p(
    class = "alert alert-info",
    htmltools::tags$strong("No verdict policy supplied. "),
    paste(
      "Computed diagnostics do not imply PASS. Missing evidence does not",
      "establish absence of a problem."
    )
  )))
}
htmltools::tagList(notices)
```

```{r findings}
htmltools::tags$ul(lapply(report_findings(result), htmltools::tags$li))
```

Survey changes describe observed pre/post differences. They do not establish why views changed. Dialogue statistics describe recorded speech. Annotation results depend on supplied coding. D, P and H describe attitudes; their signs are not grades for deliberation.

```{r summary}
s <- report_summary(result)
if (nrow(s)) {
  if (nrow(s) <= 20) {
    gt::gt(s) |> gt::fmt_number(columns = c(estimate, coverage), decimals = 3)
  } else {
    show_table(s)
  }
}
```

## Learning and opinion change

Points show separate event–item changes. Items need not measure the same construct; the report does not average them into a common success score. The main analysis uses the membership setting recorded below. Cluster or survey intervals appear in the diagnostic table only when their assumptions were explicitly declared.

```{r outcomes}
report_plot(result, c("knowledge_gain", "opinion_change"), "Changes by event and item")
```

H is the decrease in within-group attitude dispersion. Positive P is movement away from the baseline side's midpoint. Positive D is movement toward the explicitly designated advantaged reference's baseline view. Baseline ties can make a direction undefined.

```{r movements}
report_plot(result, c("H", "P", "D"), "Attitude movement within events")
```

## Response coverage

Attrition is post-wave missingness among observed baseline respondents. It does not count people absent from both survey waves. Missingness can alter the population described by a change estimate; neither paired analysis nor robust standard errors establishes ignorable attrition.

```{r attrition}
report_plot(result, "post_attrition", "Post-wave attrition")
```

## Membership sensitivity

When an available-wave sensitivity run is supplied, this table compares it with
the main event–item results. Differences can reflect changing respondent
composition. Neither agreement nor disagreement establishes ignorable attrition.

```{r sensitivity}
if (!is.null(result$sensitivity)) {
  other <- result
  other$metrics <- result$sensitivity
  other <- report_summary(other)
  main <- report_summary(result)
  keys <- c("event", "item", "metric", "contrast_id")
  other <- other[c(keys, "estimate")]
  names(other)[names(other) == "estimate"] <- "available_estimate"
  comparison <- dplyr::left_join(main, other, by = keys, relationship = "one-to-one")
  comparison$available_minus_main <- comparison$available_estimate - comparison$estimate
  show_table(comparison)
} else {
  htmltools::tags$p("No separate membership sensitivity run was supplied.")
}
```

## Participation and exchange

Speaking concentration and subgroup differences are diagnostics to investigate. Perfectly equal airtime is not imposed as a quality target. Argument coverage refers to the supplied inventory; it cannot establish that the inventory contains every important argument.

```{r participation}
report_plot(result, c("max_speaker_share", "voice_ratio", "silent_fraction"), "Participation")
```

```{r exchange}
report_plot(
  result, c("argument_coverage", "reason_giving", "counterargument_response_rate"),
  "Arguments and responses"
)
```

## Evidence available

“Unavailable” means required inputs are missing. “Unassessable” means inputs exist but usable observations, definitions or inferential assumptions are insufficient. Each analysis lists its requirements.

```{r capabilities}
show_table(result$capabilities[c("event_id", "layer", "analysis", "status", "reason")])
```

## Diagnostic explorer

Filter by event, item, metric or subgroup. CSV and Copy export the filtered rows. The table includes denominators, coverage, units, methods and reasons for unassessable results. Raw and Holm-adjusted p-values are separate; absent a declared testing family, tests are exploratory.

```{r diagnostics}
show_table(m[setdiff(names(m), "person_id")])
```

## Policy evaluations

Rules are evaluated separately. NOT_TRIGGERED means the conditions were not met; it does not mean PASS. NOT_ASSESSED means required evidence was missing or insufficiently covered.

```{r policy}
if (!is.null(result$policy)) {
  htmltools::tagList(
    htmltools::tags$p(result$policy$version, ": ", result$policy$rationale),
    show_table(result$policy_results)
  )
} else {
  htmltools::tags$p("No policy was supplied.")
}
```

## Definitions and reproducibility

```{r definitions}
htmltools::tagList(lapply(result$contrasts, function(ct) {
  htmltools::tags$p(
    htmltools::tags$strong(ct$id), ": ", ct$rationale,
    ". Reference designated advantaged: ", ct$reference_advantaged
  )
}))
```

```{r provenance}
show_table(data.frame(
  table = names(result$metadata$input_hashes),
  sha256 = unname(result$metadata$input_hashes)
))
```

```{r configuration}
show_table(data.frame(
  setting = names(result$metadata$config),
  value = vapply(result$metadata$config, function(z) {
    paste(utils::capture.output(utils::str(z)), collapse = " ")
  }, "")
))
```

```{r ledger}
if (!is.null(result$metadata$provenance$ledger)) show_table(result$metadata$provenance$ledger)
```

```{r validation}
show_table(result$validation)
```

```{r evidence, results='asis'}
if (include_evidence) {
  cat(paste(
    "<h2>Source evidence</h2><p>Includes supplied participant",
    "identifiers and source excerpts.</p>"
  ))
  for (nm in names(result$evidence)) {
    d <- result$evidence[[nm]]
    if (is.null(d)) next
    cat(as.character(htmltools::tags$h3(nm)))
    cat(knitr::kable(d, format = "html", escape = TRUE, row.names = FALSE))
  }
} else {
  cat(paste(
    "<p>Source excerpts and person-level records are omitted. The",
    "saved R result retains supplied evidence and identifiers.</p>"
  ))
}
```

```{r session}
utils::sessionInfo()
```
