---
title: "Input schema"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Input schema}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(deliberately)
```

An input is a named list of data frames with schema version `1.0`. Supply the
tables needed by your analyses; do not fill absent tables with invented records.
The `events` table anchors all IDs. CSV input uses one recognized table per file,
for example `people.csv`, and the literal `NA` for missing values. ID columns
are read as character to preserve leading zeroes.

```{r}
schema <- data_schema()
knitr::kable(data.frame(
  table = names(schema),
  key = vapply(schema, function(s) paste(s$key, collapse = ", "), ""),
  required_columns = vapply(schema, function(s) paste(s$fields, collapse = ", "), "")
))
```

## Identity and measurement units

All IDs are scoped to an event; use pseudonymous stable person IDs. IDs may repeat
across events. Primary keys must be complete and unique. Foreign keys must match
supplied parent records. Extra columns are preserved. Unknown tables are errors.
People have roles `participant`, `moderator`, `expert`, or `observer`; participant
attributes such as education, gender or income are additional columns on `people`.
The package never derives those attributes from names or speech.

An episode pairs one pre and one post survey wave. A session is one timed
discussion, plenary or expert session. Multiple sessions can belong to an episode.
`assignments` records one intended and actual group per participant per episode.
If group assignments change between survey contrasts, use separate episodes.
Session attendance remains the authority for transcript participation.

`recruitment` has one row per person, with the last observed recruitment `stage`
and logical `attended`. NA attendance is unknown, not absence. Recruitment stage
counts describe the supplied last-stage classification, not a reconstructed
recruitment funnel.

## Time, attendance and recording completeness

Session `start`/`end`, turn timestamps, coverage intervals, attendance `enter`/`exit`
and material `available_at` use seconds from one declared event origin. Record
that origin and timezone in `provenance`; concurrent sessions share a clock.
End points must exceed start points. Missing paired endpoints are permitted for
unknown session/attendance/turn times; coverage intervals must be known.

Attendance supports multiple intervals per person and session, each with an
`interval_id`. Status is `present`, `absent` or `unknown`. Repeated or overlapping
present intervals are unioned. Speakers who are not participants do not enter
participant airtime denominators. Present participants with no turns contribute
zero turns. If a participant spoke but is missing from the present roster,
correct the roster before interpreting participation.

`coverage` contains recorded intervals, not gaps. The package unions overlapping
intervals. Turn `sequence` is a positive integer, unique within session; it is
required even without timestamps. Overlapping turn intervals are allowed across
speakers. A missing speaker ID is permitted but flagged; it prevents complete
participant shares and silence classification.

Optional `turns.start` and `turns.end` unlock airtime; word shares are separate.
Optional logical `argument_coding_complete` declares that a turn was exhaustively
mapped to the supplied inventory, including an explicit finding of no match.
It is not a recording-completeness declaration.

## Survey items and scales

Each response is one person × episode × item × wave. Missing responses may be
explicit NA rows. Include those rows for every intended measurement when you want
missing-response coverage to use the full intended denominator. Raw `value` is
preserved; normalized values are derived during the audit. Out-of-scale values
are errors, so recode survey missing-value sentinels before constructing a bundle
and record the recode ledger in provenance.

Items have `kind` equal to `attitude`, `knowledge` or `experience`, finite `lower`
and `upper` endpoints, and `direction` of 1 or -1. Normalization is
`(value - lower) / (upper - lower)`; direction -1 reverses the result.
`midpoint` is the substantive neutral point in raw units. It may be NA; the package
does not replace it with the arithmetic midpoint. P then remains unassessable.

Knowledge items additionally specify `scoring`:

* `binary_key`: supply numeric `correct_value` in original response units.
* `proportion_correct`: declare an already-scored proportion, with endpoints 0/1
  and direction 1. Wrong and missing answers remain distinct.

With multiple knowledge items, `__knowledge_mean__` is the derived equally weighted
person-level mean, requiring the complete item set at each wave. Optional logical
`include_in_knowledge` chooses the set; omit it to include all knowledge items.
Do not include both an aggregate score and its component items in the same index.
The derived item ID is reserved. Aggregate source scores alone do not identify
item-specific learning.

Waves record explicit `phase` (`pre`, `post`, `other`) and a human-readable `timing`.
At most one pre and post wave per episode is allowed. To analyze another post
wave, construct another explicitly identified episode/contrast.

## Benchmarks and design assumptions

Each benchmark identifies a `variable`, `target`, `population`, and optional
categorical `level`. With `level = NA`, `target` is a numeric mean and `sd` is its
target-population SD. With a category level, `target` is a proportion. Different
category levels require distinct benchmark IDs. Reference proportions are not
silently renormalized. Marginal comparisons do not establish joint balance.

Variables name people-table attributes or normalized baseline items using
`item:episode_id:item_id`. Explicit `baseline_predictors` in `audit_config()` use
the same names. The researcher must verify that attributes are measured before
deliberation. Attendance prediction never selects predictors from outcomes.

`sampling` contains the full probability-sample roster with positive `weight`,
`psu` and `stratum`. For independent unstratified sampling, use each person's ID as
PSU and one common stratum. Optional `fpc` follows `survey::svydesign` conventions.
Set `probability_sample = TRUE` only when justified. The supported variance model
is single-stage cluster/stratified sampling; absent FPC uses with-replacement PSU
variance. Lonely PSUs produce non-estimability rather than a hidden adjustment.

`randomization.mechanism` supports `complete_fixed_sizes` and
`blocked_fixed_sizes`. Each implies uniformly random label allocations preserving
observed group counts, globally or within supplied blocks. These are not inferred
from balance. Other mechanisms remain descriptive. Tests require a complete
paired assignment roster and matching intended/actual groups.

## Arguments, source passages and annotation provenance

`materials` identifies source passages by source ID, version and event-time
availability. Arguments have topic, perspective, text, optional passage reference,
and attributed review (`reviewed`, `reviewer`). Perspectives need not be binary.
The denominator is the declared inventory for the session topic. That inventory
is not automatically a complete or balanced set of strong arguments.

`argument_edges` connects inventory IDs with researcher-supplied relations such
as `supports`, `objects_to` or `responds_to`. Optional `node_type` on arguments
distinguishes `argument` from `reason`, `evidence`, `objection` and `response`;
coverage uses argument nodes. With no node_type, all rows are argument nodes.

Annotations target `turn`, `passage` or `argument` IDs. Each contains `code`,
`value`, `coder`, `source_type` (`human` or `model`), `codebook_version` and
`review_status` (`unreviewed`, `accepted`, `rejected`, `adjudicated`). Model records
also need `model` and `prompt_version`; optional `confidence` is preserved, not
used as accuracy. Optional `start_char`/`end_char` are inclusive 1-based character
offsets. Supply a full-turn target when the code applies to the complete utterance.

Built-in turn codes:

| Code | Values and denominator |
|---|---|
| `recommendation` | 0/1; identifies turns containing policy recommendations |
| `reason_level` | 0 claim; 1 reason; 2 evidence/example; 3 response to another reason |
| `evidence_present` | 0/1; direct evidence coding, including for responsive turns |
| `counterargument` | 0/1; identifies counterarguments |
| `response_observed` | 0/1 on a counterargument; explicit assessment of whether it received a substantive response |
| `engages_previous` | 0/1 on a recommendation; explicit prior-argument engagement |
| `personal_attack`, `dismissive`, `conformity_pressure` | 0/1 on coded turns |
| `moderator_correction` | 0/1 on coded turns |
| `interruption_given`, `interruption_received` | 0/1 on coded turns; incidence, not event counts |
| `floor_attempt`, `floor_success` | 0/1; success probability conditions on a coded attempt |
| `stance` | -1/0/1 according to a declared topic-specific orientation |

Reason level 3 indicates responsiveness; it does not logically require evidence.
The package reports evidence separately using explicit level 2 codes.
These are package conventions requiring an event-specific codebook, not a
validated implementation of a published DQI instrument. Additional codes are
retained for extensions. Conflicting selected codes are omitted until a unique
adjudicated value resolves them. Review and exact agreement are reported separately.

Links have `from_turn`, `to_type` (`turn` or `argument`), `to_id`, `relation` and the
same coding provenance. Coverage recognizes argument links `expresses`, `supports`
and `rebuts`. Responsiveness recognizes turn links `substantive_response`,
`acknowledges` and `rebuts`. Within a session the target must precede the response.
An absent link is not automatically negative evidence. Cross-session links remain
in the evidence graph; within-session response rates use within-session targets.

For opposing-argument opportunity, attitude items additionally need `topic_id`,
`perspective_positive` and `perspective_negative`, defined on the direction-adjusted
scale. A participant at the neutral midpoint has no designated opposing direction.
This diagnostic uses vetted arguments and timestamp overlap with attendance.

## Working with incomplete data

```{r}
x <- example_deliberation()
x$tables$turns <- NULL
x$tables$annotations <- NULL
x$tables$links <- NULL
available_analyses(x)[, c("analysis", "readiness", "reason")]
```

Remove dependent annotation tables when removing source records. Invalid joins
stop the audit; merely absent optional inputs do not. Validation findings have
machine-readable codes and source row numbers. No missing input is a PASS.
