---
title: "Methods and interpretation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Methods and interpretation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(deliberately)
```

## What is being estimated?

The default target is a descriptive quantity for the observed event, session,
group or subgroup. Equal participant weights are used for survey summaries;
`weighted = TRUE` uses supplied weights for survey outcomes and benchmark
comparisons. Dialogue metrics continue to describe observed participants.
No opinion direction is defined as intrinsically good or bad.

Each result names its analysis, metric, unit IDs, estimate, units, denominator,
usable observation count, coverage, computation status and method. Missing or
undefined estimates remain NA with a reason. Full and partial cases must not be
silently combined to calculate a headline success rate.

## Sample, selection and assignment

Benchmark differences are sample minus target. Standardized differences divide
by the supplied target-population SD; categorical levels use the Bernoulli target
SD. The convention is a target-standardized difference, not a pooled-sample SMD.
If recruitment attendance is supplied, sample benchmarks use known attendees;
otherwise they describe the supplied participant roster. Missing values are
excluded separately and the denominator is reported. A benchmark with zero target
variance has an undefined standardized difference but an estimable raw difference.

Attendance comparisons contrast known attendees and nonattendees. Logistic
prediction uses only explicitly declared baseline variables and complete predictor
cases. Stratified cross-validation uses up to five folds, bounded by the smaller
attendance class. Fewer than two members in either class, separation-related
nonconvergence, unseen factor levels or failed predictions make AUC unassessable.
Predictive performance is not a test of ignorability or a measure of selection
bias. No default AUC warning threshold is supplied.

Assignment differences compare each intended group's baseline mean with the
episode-wide mean, divided by the episode baseline SD. Actual assignments are
retained for observed group outcomes. Differences between intended and actual
assignment are separately counted. Balance never establishes randomization.

## Participation

For each session, present participants define the roster, including people with
zero turns. Per-person speaking time is the union of that person's recorded turn
intervals. Participant shares divide these durations by their sum; simultaneous
speech by different people contributes to each person's time. The talk-time Gini
is `sum(abs(outer(shares, shares, "-"))) / (2 * n)`. Perfect equality is not a
normative target imposed by the package.

Word counts split nonempty text on whitespace. They are a separate, language- and
transcription-dependent measure, not an estimate of elapsed speech. Pairwise
overlap sums intersections for different speakers; three simultaneous speakers
create three pair contributions. It is not an interruption count. Coded
interruptions represent incidence on coded turns, not inferred intent.

Silent fraction requires full session recording coverage and identified speakers.
Unknown attendance does not add silent participants. Partial recordings can yield
observed talk shares but cannot establish complete-session silence. The voice
ratio is mean focal speaker seconds divided by mean reference speaker seconds;
unequal attendance duration remains a substantive qualification. A zero reference
mean makes the ratio undefined.

## Deliberative exchange

Reason giving is the proportion of explicitly coded recommendations with a coded
reason level of at least 1. Evidence giving uses an explicit `evidence_present`
code where available, otherwise level 2 means evidence and levels 0/1 mean none;
level 3 alone leaves evidence unknown. An argument responding to a reason need
not cite evidence.

Counterargument response rates use explicitly coded `response_observed`, augmented
by accepted substantive-response links. Absence of a link does not imply no
response. Links to other turns also expose cross-person uptake. Personal attacks,
dismissiveness and pressure are rates among coded turns, with coding coverage
reported against the transcript. Moderator/expert stance means use the codebook's
declared orientation; neutrality is not inferred from low speaking time.

Argument coverage is the fraction of the declared topic/perspective inventory
linked to transcript turns. Exact session coverage requires completed argument
coding and complete recording; otherwise only an observed lower bound is returned.
Vetted coverage restricts to attributed reviewed arguments. Briefing coverage
requires a linked source passage available no later than session start.

Opposing-argument opportunity joins a directional pre-view, an explicitly mapped
opposing perspective, a vetted argument and overlapping attendance. It establishes
opportunity to encounter, not comprehension, attention, agreement or persuasion.

Annotation statistics are conditional on the provided labels. Repeated codes from
multiple coders produce an exact agreement diagnostic, not chance-corrected
reliability. Contradictory codes require adjudication; model confidence neither
resolves disagreements nor widens or narrows survey intervals. No inference about
latent deliberative quality is claimed without a measurement-validation design.

## Opinion change, H, P and D

Let `pre` and `post` be normalized group means and `ref` a fixed baseline
reference. Signed movement is `(post - pre) * sign(ref - pre)`. If the reference
equals the initial group mean within `1e-12`, direction is undefined. Genuine
zero movement with a defined direction is zero. Movement past a reference retains
the baseline direction; it is not a change in absolute distance.

* `H = SD(pre individuals) - SD(post individuals)`; positive is homogenization.
* `P = -signed_movement(group pre, group post, midpoint)`; positive is movement
  away from the baseline side's substantive midpoint.
* `P_absolute = abs(post - midpoint) - abs(pre - midpoint)` is a separate measure
  that differs when a group crosses the midpoint.
* `D = signed_movement(contrast-population pre, contrast-population post,
  advantaged-reference pre)`. Both focal and reference groups must be represented.
  People outside the contrast are excluded, and the result says so.
* `D_focal` replaces the moving population with focal members, retaining the
  advantaged reference's baseline position.

Unweighted SD uses the ordinary sample denominator. Supplied-weight SD uses
`sum(w * (x - weighted_mean)^2) / (sum(w) - sum(w^2) / sum(w))` under a square root.
This is a descriptive weighted SD, not a design-corrected estimator of population
variance. Units for H/P/D are fractions of the declared scale range.

Paired membership is the default: each item's pre and post summaries use the same
people with both observations. `membership = "available"` is an explicit
sensitivity calculation using each wave's observed respondents. It can mix
composition change with attitude change. `n` reports paired people except on
wave means; denominator is the supplied response roster for that item and unit.
Event-level H/P/D operate on event-level observations; they are not averages of
group-level H/P/D.

Knowledge is scored from an explicit key or supplied correct-answer proportion.
Gain and fraction learning use observed paired scores. Standardized gain divides
mean change by baseline score SD; zero baseline variance leaves it undefined.
Subgroup knowledge-gap change is `(focal - reference) post - (focal - reference) pre`.
A negative value is not automatically improvement: interpretation depends on the
initial gap's sign. Raw scores and their item-level changes remain inspectable.

The signs and tie conventions follow the corrected `distortions` implementation
of [Luskin et al.](https://doi.org/10.1017/S0007123421000168). These measures describe
attitudes, not participation equality, coercion or the merits of arguments.

## Group heterogeneity and inference

Group partial R-squared is the reduction in residual sum of squares when group
indicators are added to `post ~ pre`, divided by the baseline model's residual sum
of squares. Group adjusted deviations are group means of baseline-model residuals.
These are in-sample descriptive associations, with no default anomaly threshold.
The statistic can be large with many small groups; assignment-based comparison
requires the actual supported randomization mechanism.

Randomization tests evaluate the sharp null that any allowed group assignment
would leave every participant's observed outcome unchanged. Permutations preserve
fixed group sizes, within blocks when declared. The Monte Carlo p-value is
`(1 + number of draws >= observed statistic) / (B + 1)`. The full paired assignment
roster is required; missing outcomes and assignment deviations block the test.
The statistic is recomputed after every reassignment, keeping baseline measures
fixed. These tests do not identify which interaction or moderator caused a shift.

With episode-level outcomes, moderators assigned to groups are generally
confounded with those groups. Replicated moderators get descriptive adjusted
associations. The package explicitly refuses a separate moderator-effect claim
when that effect cannot be distinguished from group exposure; multiple moderators
per group require finer outcome/exposure information.

Sampling intervals use the supplied full design roster and a paired-response
domain, retaining design structure before subsetting. Taylor linearization from
`survey` gives the SE, and a t interval uses domain design degrees of freedom.
Weights do not establish response ignorability. Missing probability-sampling
declaration, incomplete design fields, lonely PSUs or no residual design degrees
of freedom yield unassessable inference. These intervals condition on scoring and
do not incorporate annotation-model uncertainty.

## Attrition and model-based cluster inference

`post_attrition` is the proportion of observed baseline respondents lacking a
usable post score, by event, group, item and declared subgroup. Its coverage is
the baseline-observed fraction of the supplied item response roster. People
absent from both waves cannot be recovered from that roster. Available-case
change is a composition sensitivity calculation, not an attrition correction.

`cluster_inference()` requires cluster columns, a target of inference and a
reason to treat clusters as independent. It fits paired change using
`clubSandwich` CR2 covariance and Satterthwaite degrees of freedom. The intercept
estimates mean change; a focal indicator estimates the focal minus reference
change directly, excluding people outside the contrast. Coverage uses the
corresponding event or contrast response roster. Supplied weights enter weighted
least squares when requested. Multiple cluster columns identify a single
composite cluster, not multiway clustering. Effective degrees of freedom and the
number of clusters accompany every result; unidentified or degenerate models are
unassessable. An SE no greater than machine epsilon times the largest absolute
change is treated as numerical zero; individual-level residual variation cannot
substitute for between-cluster variation.

These model-based intervals describe a declared repeated-sampling process. They
do not establish population representativeness or a causal effect of attending
deliberation. Use the separate `survey` design path for probability-sampling
inference. The optional `inst/examples/wild-bootstrap.R` example compares a
clustered subgroup change difference with `fwildclusterboot`; it is a tested
sensitivity example, with its backend installed separately from the author's
repository. No automatic choice of inference method is made from the p-value.

```{r}
detectable_change(n = 100, sd_change = 0.2, design_effect = 1.5)
```

This precision calculation is a two-sided normal planning approximation under the
supplied change SD and variance inflation. It does not report retrospective power
from the observed opinion change. Subgroup calculations use subgroup n and
explicitly chosen assumptions.

## Policies and claims

Policies record version, rationale, scope, required metrics, thresholds and
coverage requirements. Conditions sharing a rule ID are combined with AND. `aggregation`
determines all/any evaluation among matching estimates, after optional item,
contrast, detail and person selectors. Every matched value must be assessable
before a condition can trigger, including `any` conditions. Missing coverage does
not meet a threshold of zero.

Verdicts are per rule, not a hidden overall grade. `NOT_TRIGGERED` is not PASS.
Policies can combine concentration, missing counterarguments, learning and opinion
change, but the causal or normative interpretation remains the researcher's.
Raw p-values remain available. `test_families` declares named, nonoverlapping
sets of metric names. Holm adjustment pools every matching event, episode, item
and contrast row in each family. Unassessable members remain NA and count toward
family size. Define families before inspecting results; adjustment does not make
post hoc selection confirmatory.

The software records seed, configuration, table hashes, evaluated memberships,
evidence provenance and R session information. Reproducibility does not imply
prospective preregistration or blinded policy selection.
